Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 paper.tex
Updates from Overleaf

The advantage of our estimation strategy is that we do not rely on identification from an instrument or the structure of a model, but from the fact that the trajectory that a household takes in their adoption decisions through time is an informative source of identifying information. See \cite{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc} for more information on the assumptions involved for the Group Random Coefficients estimator. Table \ref{tbl:trajectories} maps out the

>>>>

The advantage of our estimation strategy is that we do not rely on identification from an instrument or the structure of a model, but from the fact that the trajectory that a household takes in their adoption decisions through time is an informative source of identifying information. See \cite{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc} for more information on the assumptions involved for the Group Random Coefficients estimator.

Table \ref{tbl:Trajectories} maps out the frequencies of the different trajectories present in the data, sorted by frequency. The largest portion of the data are those that do not adopt improved maize seed at all, followed with sharp decline, to those that use improved maize seed in every period. Interestingly, adoption trajectories seem to be more popular for later adoptions than earlier ones.

\input{results/tables/traj}
